---
title: "R Notebook"
output: github_document
---

Loading packages needed:
```{r setup_workspace, message= FALSE}
library(tidyverse)
library(ggplot2)
```

Reading in data file and quickly checking it:
```{r}
jam_covid<-read.csv("coronavirus_jamaica.csv")
head(jam_covid)
```

```{r}
jam_covid$Date <- as.Date(jam_covid$Date, format="%m/%d/%y")
```

Plot of Daily Covid Case Count in Jamaica:
The bar graph below shows the daily incidence of Covid-19 cases over the month of August 2021. This dataset was obtained from the Ministry of Health (MOH) monitoring program.  
```{r}
covid_plot<-ggplot(data=jam_covid, aes(x = Date, y = New_Cases)) +
  geom_bar(stat = "identity") +
  scale_x_date(breaks = jam_covid$Date) +
  theme(axis.text.x = element_text(angle = 90, size=5)) +
  xlab("Dates") +
  ylab("Number of New Cases") +
  ggtitle("Covid-19 Cases in Jamaica - August 2021")
covid_plot  
```


This graph shows an alarming trend where daily Covid-19 cases are increasing quickly over a month period. If this trend continues, then eventually our healthcare system will overburdened. 

