---
title: "HW 5"
output: github_document
author: Zabrenna Griffiths
---

```{r message= FALSE, warning= FALSE}
# library(diamonds)
library(ggplot2)
library(tidyverse)
library(dplyr)
```

1. Print a data frame that contains the simple count of diamonds in each “cut” (“Fair”, “Good”, etc.).
```{r}
diamonds %>% count(cut)
```

2. The diamonds data set is reasonably big, which is a bit of a pain. Use dplyr functions to create a that contains 1% of the rows of diamonds, randomly sub-setted.
```{r}
random_sampling <- sample_frac(diamonds, 0.01)
random_sampling
```

3. Calculate the average size of the 100 largest diamonds in each clarity category.
```{r}
top_100 <- diamonds %>% 
  group_by(clarity) %>%
  slice_max(carat, n= 100) %>%
  summarise(mean(carat))
top_100
```

4. Make two scatter plots:
* plot of the x dimension vs the y dimension
```{r}
ggplot(data=diamonds, aes(x=x, y=y)) +
  geom_point() 
  # xlim(3,11) +
  # ylim(0,20)
```

* plot of the x dimension vs the z dimension
```{r}
ggplot(data=diamonds, aes(x=x, y=z)) +
  geom_point()
```

5. Note that x, y, and z here refer to the length, width, and depth of the diamond in mm. Are there any data points that you find suspicious? If so: create a new data frame, with these questionable points removed.
```{r}
diamonds2 <- diamonds %>% 
  filter(x <= 10 & x >3 & y <= 20 & y > 2.5 & z <= 10 & z >2)
```

#### Creating New Plots To Visualize Data After Removing Outliers
```{r}
ggplot(data=diamonds2, aes(x=x, y=y)) +
  geom_point()
```

```{r}
ggplot(data=diamonds2, aes(x=x, y=z)) +
  geom_point() 
```

