---
title: "HW 5"
output: github_document
author: Zabrenna Griffiths
---

Loading necessary packages
```{r message= FALSE, warning= FALSE}
library(tidyverse)
```

Loading in data file
```{r}
justsamples <- read.csv("samples_taxa.csv", stringsAsFactors= FALSE)
# head(justsamples)
```

Just some data selection to only work with aerobic samples
```{r}
aerobicsubset <- justsamples[which(justsamples$oxygen==2),]
# head(aerobicsubset)
```

Making my bad plot showing relative abundances of different bacterial orders in an aerobic microcosm experiment. However, you would not immediately know that because there's no title on this plot (Wilke pg. 22)

```{r}
aer_plot <-ggplot(aerobicsubset, aes(x= day, fill = Taxa, y = Abundance))+
  geom_bar(stat= "identity")
aer_plot
```
  
  This plot is made with the ggplot color default which is super unhelpful in this case as it uses a continuous color scale. This makes it difficult to differentiate between bacterial orders for a person with normal vision. This plot would probably be even more difficult for a person with color blindness to interpret as the color scale also includes a lot of close shades of red and green. The data looks like its intermingling instead of being distinctive (Wilke, 19).  
  This plot is also a little messy and needs some revision to portray the result (Tufte, 105). The x-axis labels are overlapping and difficult to read. They are also arranged in the default alphabetical order which is not the best way to arrange this dataset (Wilke, 23). Both Tufte and Wilke advise against clutter and maximizing the data-ink ratio.   

Making a better plot goals:  
* add title  
* fix axis angles  
* change order of labels on x-axis  
* change colors of bars  

```{r}
color_scale = c("#d0f7ed","#004949","#009292","#ffb6db","#490092","#006ddb","#b66dff","#6db6ff","#b6dbff",
 "#920000","#924900","#db6d00","gray50","#24ff24","#ffff6d", "#7B4EC2", "#C17600", "#250977", "#00914F", "#AADA52", "#BB0054", "#FCCD83", "#5B1549", "#E2D84F", "#5B005B", "#BDDF8E", "#5A0811", "#007AE8", "#425800", "#FF69C5", "#730006", "#C7E9B4", "#762A83", "#FFF7BC", "#D9D9D9", "#000000", "#F16913", "#003C30", "#FFF7FB", "#8C6BB1", "#FD8D3C", "#F7F7F7", "#EF3B2C")
```


```{r}
orderedsubset <- aerobicsubset %>%
arrange_at("Taxa", desc) %>%
  arrange_at("Abundance")
```


```{r}
aer_plot_new <-ggplot(orderedsubset, aes(x= day, fill = Taxa, y = Abundance)) +
  geom_bar(stat= "identity", colour="black", width = 0.75) +
  theme(axis.text.x = element_text(angle = 90, size = 12, colour = "black", vjust = 0.5, hjust = 1), 
        axis.title.y = element_text(size = 12), legend.title = element_text(size = 10), 
        legend.text = element_text(colour = "black", size = 8.5), 
        axis.text.y = element_text(colour = "black")) +
  ggtitle("Relative Abundance of Dominant Orders in Aerobic Microcosms") +
  labs(y= "Relative Abundance(%)", x = "Days") +
  scale_fill_manual(values = color_scale) +
  scale_x_discrete(limits = c("Initial Control", "Day 0", "Day 5", "Day 10", "Day 15", "Day 115", "Final Control"))
aer_plot_new
```
  
My "good" plot could still use some work to increase the plot size.  

