---
title: "HW 8"
output: github_document
author: Zabrenna Griffiths
---

# Question 1
Using the diamonds data set, make a data frame that shows the slope of the relationship of price as a function of weight (carat) for each unique color, in decreasing order of slope

How does price change for with weight/carat for each diamond color?
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(modelr)
library(purrr)
```

```{r message=FALSE, warning=FALSE}
by_color <- diamonds %>% 
  group_by(color) %>% 
  nest()

# Function to create a linear model of price as a function of weight (carat) 
price_for_carat <- function(df) {
  m<- lm(price ~ carat, data = df)
  m
}
# summary(price_for_carat)

# Applying function to by color database 
by_color <- by_color %>% 
  mutate(fit = map(data, price_for_carat))

# Making function to extract slope
getslope <- function(fit_obj) {
  slope <- coef(fit_obj)[2]
  slope
}

# Applying this to dataframe
by_color <- by_color %>% 
  mutate(slope = map_dbl(fit, getslope))

fit <- unnest(by_color, data)
head(fit)

# Plot predictions vs carat for each color
ggplot(fit, aes(x=carat, y=price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~color)
```

# Question 2 
The DNase dataset in the datasets package (which automatically loads when you load R) has examples of ELISA band optical density as a function of protein concentration, for 12 different runs. These relationships are clearly nonlinear (please plot density as a function of conc to see for yourself!).
```{r}
library(nls2)
```

```{r}
DNase %>%
  ggplot(aes(conc, density)) + geom_point()
```

Non-linear Least Squares Model:
```{r}
nls_mod <- formula(density ~ beta_1 * sqrt(conc) + beta_0)

single_sqrt_model <- function(DNase) {
  nls2(nls_mod, 
  data = DNase, 
  start = list(beta_1 = 0.53, beta_0 = 0.19))
}
```

Monod Model:
```{r}
monod_eq <- formula(density ~ (conc * dmax) / (conc + k))

monod_model <-  function(DNase) {
  nls2(monod_eq, 
  data = DNase, 
  start = list(dmax = 0.09, k = 1.12))
}
```

Your assignment is to use list-columns to create a separate square root model and monod model for density as a function of concentration, for each Run
```{r}
# Sorting out by run and making nested df
by_run <- DNase %>% 
  group_by(Run) %>% 
  nest()
```

```{r}
# Applying Square Root Model to df
ssrt <-  by_run %>% 
  mutate(model = map(data, single_sqrt_model))
                     
glance_ssrt <- ssrt %>% 
  mutate(glance = map(model, broom::glance)) %>% 
  unnest(glance)

glance_ssrt %>%
  group_by(Run) %>%
  arrange(AIC) %>%
  head()
```

```{r}
# Applying Monod Model to df
mnd <-  by_run %>% 
  mutate(model = map(data, monod_model))
                     
glance_mnd <- mnd %>% 
  mutate(glance = map(model, broom::glance)) %>% 
  unnest(glance)

glance_mnd %>%
  group_by(Run) %>%
  arrange(AIC) %>%
  head()
```

The Monod model has lower AIC values than the Square-root model. Therefore, the Monod model is a better fit to the data.
```{r message=FALSE, warning=FALSE}
library(cowplot)

p1 <- ggplot(glance_mnd, aes(x = Run, y = AIC)) +
  geom_col() +
  scale_y_reverse() +
  scale_x_discrete(limits=c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11")) + 
  ggtitle("AIC Values - Monod Model")

p2 <- ggplot(glance_ssrt, aes(x = Run, y = AIC)) +
  geom_col() +
  scale_y_reverse() +
  scale_x_discrete(limits=c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11")) + 
  ggtitle("AIC Values - Square Root Model")

plot_grid(p1, p2)
```


